---
title: "CCF Color Palette"
author: "Emily C. Zabor"
date: "Last Updated: `r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ccf_color_palette}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
options(rmarkdown.html_vignette.check_title = FALSE)

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ezfun)
library(ggplot2)
```


## Introduction

This vignette gives a short example on usage of the `ccf_color_palette` functionality. The goal of the `ccf_color_palette` functions is to give users access to Cleveland Clinic brand colors for use in plotting with `ggplot2`. 

The code behind this color palette is largely based on the code from the Wes Anderson color palettes for R: [https://github.com/karthik/wesanderson](https://github.com/karthik/wesanderson) and a previous brand color palette I created at Memorial Sloan Kettering Cancer Center.


## The colors

Details about the CCF brand colors can be found at the [OnBrand website](https://onbrand.clevelandclinic.org/get-the-basics/#color-palette).

On a basic level, the CCF brand colors are stored as named values. You can see a complete list:

```{r}
ccf_cols()
```

You can access the hex color for a specific color:

```{r}
ccf_cols("ccf_green")
```

You can access the hex color for multiple colors:

```{r}
ccf_cols("ccf_blue", "ccf_green")
```


## Palettes

There are six color palettes available.

You can view a list of the color names and hex codes for a specific color palette:

```{r}
ccf_palettes[["main"]]
```

And you can also view the colors in a plot window.

### main

The `main` color palette is based on the primary and seconary CCF brand colors.

```{r fig.height = 1}
ccf_palette("main")
```

### bright

The `bright` color palette is based on the bright supplemental CCF brand colors.

```{r fig.height = 1}
ccf_palette("bright")
```

### neutral

The `neutral` color palette is based on the neutral supplemental CCF brand colors.

```{r fig.height = 1}
ccf_palette("neutral")
```

### all

The `all` color palette contains all colors from main, bright, and neutral for when a large number of colors are needed.

```{r fig.height = 1}
ccf_palette("all")
```

### blues

The `blues` color palette only contains two colors and is meant to be used for continuous color scales where interpolation will be done between the high and low color.

```{r fig.height = 1}
ccf_palette("blues")
```

### greens

Similarly, the `greens` color palette only contains two colors and is meant to be used for continuous color scales where interpolation will be done between the high and low color.

```{r fig.height = 1}
ccf_palette("greens")
```


## Plotting

Functionality is available to plot single or multiple colors, discrete color scales, and continuous color scales.

To use a single specific color, simply reference it by name.

```{r}
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point(size = 4, color = ccf_cols("ccf_green"))
```

You can do the same to use multiple specific colors using `scale_color_manual`.

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(
    values = ccf_cols(c("ccf_green", "seagull", "maroon_flush")))
```

To use the palettes, specify a palette by name as the `values` argument to `scale_color_manual` or `scale_fill_manual`. 

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(values = ccf_palette("main"))
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(values = ccf_palette("bright"))
```

You can also pick and choose which colors you want by position in the palette.

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(values = ccf_palette("main")[c(1, 4, 6)])
```

The `scale_color_gradientn` function can be used to add colors on a continuous scale, by adding the option `type = "continuous"` to `ccf_palette()`. Interpolation between colors in the palette will be done to create a continuous scale, and this is intended for use with the `blues` and `greens` palettes.

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Petal.Length)) +
  geom_point(size = 4) +
  scale_color_gradientn(colors = ccf_palette("greens", type = "continuous"))
```








